Minimax lower bounds for source localization

### 2017-01-08 paper.tex
Fix figure positions; add extensions section.

Mosher et.\ al.~\cite{Mosher1993Error} first propounded Cramer-Rao lower bounds
for unbiased source localization algorithms. Their work also forms the basis
for setting up the source localization problem and deriving more universally
applicable bounds in this paper. The Cramer-Rao lower bound is not in itself a
completely satisfactory answer to the question of fundamental limits for source
localization accuracy. This is because Cramer-Rao bounds only apply to unbiased
estimators (or to estimators of \emph{known} bias). In practice, however, many
popular source localization algorithms have been shown to be biased, for e.g.\
the Minimum Norm Estimate (MNE)~\cite{Hamalainen1994Interpreting} is known to
bias the solution towards the surface of the head~\cite{Lin2006Assessing}. It
is also known that unbiased estimators can have worse mean-squared-error
performance than biased estimators. So Cramer-Rao bounds are useful only to a
degree, and there may be benefit in deriving bounds that hold for all
estimators.

@@

All signals on the aforementioned circular domain are of the form
$f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
represented by the impulse signal, $f(t;\theta) = \delta(t - \theta)$, where
$\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
through the diffusive medium, which, intuitively speaking, blurs the impulse.
More concretely, we assume that the medium is linear and shift-invariant, so
that it can be represented by a spatial impulse response (blurring would then
correspond to low-pass filtering). Let this impulse response be given by
$g(t)$. Then, the noiseless, continuous-space signal (post-filtering and
pre-sampling) is given by the convolution, $x(t; \theta) = (g*f)(t) = g(t -
\theta)$. Here, we further make the simplifying assumption that $g(t)$ has
restricted support, so that aliasing effects are avoided, and $x(t; \theta)$ is
always well-defined. To be precise, $g(t) = 0$ when $\abs{t} > w/2$, where the
``width'' $w$ of the impulse response satisfies $w < T / 2$ (the reason for the
factor of $1/2$ will become clear in a later section).

@@

Consider the following estimation problem: we have $n$ i.i.d.\ random samples
$Y^n$ from a distribution $P$, which is indexed by a parameter $\theta \in
\Theta$.  Denote the set of these distributions by $\mathcal{P} = \{P(\theta) :
\theta \in \Theta\}$. Suppose we now wish to estimate $\theta$ from $Y^n$.
Define a loss metric $\rho(\theta, \hat\theta)$. For this metric, we can define
the minimax risk over all possible estimators $\hat\theta(Y^n)$ and all
possible $\theta \in \Theta$:
\begin{equation} \label{eq:minimax-expr}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \inf_{\hat\theta} \sup_{\theta \in \Theta} \mathbb E[\Phiorho (\hat\theta(Y^n), \theta)]
\end{equation}
where $\Phi$ is any non-decreasing function (e.g. $\Phi(\rho) = \rho^2$) and
$Y^n$ is the random vector corresponding to a noisy realization of sensor
values.

@@

We now need to lower bound the probability of error in the hypothesis testing
problem. The simplest way to do this is to consider a binary hypothesis test
($\abs{\mathcal{V}} = 2$) and use what is known as Le Cam's method:
\begin{theorem} \label{thm:le-cam}
	For a binary hypothesis test, i.e., $\mathcal{V} = \{0, 1\}$,
	\begin{equation}
		\inf_\psi \mathbb P(\psi(Y^n) \neq V) = 1 - \norm{P_0 - P_1}_{TV}
	\end{equation}
	where $P_i$ is short-hand for $P(\theta_i)$ and $\norm{P_0 - P_1}_{TV}$ is
	the total variation distance between the two distributions, defined as
	$\norm{\cdot}_{TV} = \frac{1}{2} \norm{\cdot}_1$.
\end{theorem}
For a proof, we refer the reader to Proposition~2.11
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:le-cam} states
that the minimum probability of error that any estimator must make in a binary
hypothesis testing problem is related to the distance between the distributions
corresponding to the two hypotheses. The closer the two distributions, the
higher the chance of making an error in distinguishing between them.

@@

\begin{IEEEproof}
Starting from equation~\eqref{eq:le-cam-bound} and working on the setting
described in Section~\ref{sec:source-localization}, we proceed to derive the
total variation distance for the distributions of interest. Using Pinsker's
inequality~\cite{Pinsker} and the convenient tensorization of the KL
divergence~\cite{tensorization}, we see that:
\begin{equation} \label{eq:pinsker-tensorization}
	\norm{P_1^n - P_0^n}_{TV} \geq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
\end{equation}
For multivariate normal distributions with the same covariance, the KL
divergence is given by
\begin{equation} \label{eq:kl-div-normal}
	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
\end{equation}
where $\v \mu_0$ and $\v \mu_1$ are the means of the two Gaussians~\cite{KLDivNormal}.

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta = \v x(\theta_0) - \v x(\theta_1)$ for brevity. Denoting the
$k$-th component of $\v\Delta$ as $\Delta(k)$, we see that
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kT}{m}; \theta_0\Big) - x\Big(\frac{kT}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(t;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\theta_1 = \theta_0 + 2\delta$ (by virtue of the $2\delta$ packing).
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ counts the number of non-zero elements in $\v\Delta$, which
is equal to the number of sensors in the total region covered by the signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ (see figures~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{T}}$, since at most a fraction $(w + 2\delta) / T$ of sensors can
lie in the region covered by the two impulse responses. The final upper bound
on $\norm{\v\Delta}^2$ is therefore
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T}} \leq 4 \kappa^2 \delta^2 \frac{m (w + 2\delta)}{T}.
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
e.g.). One part of the signal $x(t;\theta_0)$ will appear at the left edge of
the domain, and the repetition from the period $[T, 2T)$ will appear at the
right edge of the domain. Also note that the two signals $x(t;\theta_0)$ and
$x(t;\theta_1)$ overlap at most once, since $w < T/2$, as stated in
section~\ref{sec:signal-model}.

\begin{figure}[tbp]
	\centering
	\includegraphics[width=2.8in]{overlap-middle-pics}
	\caption{Depiction of the continuous-space signals produced by two
		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
		shifted impulse response, and therefore has a support of size $w$.
		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
		$\Theta$, so the signals are separated by a distance $2\delta$.}
	\label{fig:overlap-middle}
\end{figure}

\begin{figure}[tbp]
	\centering
	\includegraphics[width=2.8in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

The upper bound in equation~\eqref{eq:delta-bound} translates into a lower
bound for equation~\eqref{eq:lb-after-pinsker}:
\begin{align}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n}{2\sigma^2 T} 4 \kappa^2 \delta^2 (w + 2\delta) m} \Bigg] \\
	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2nm \kappa^2 \delta^2 (w + 2\delta)}{\sigma^2 T}} \Bigg] \label{eq:lb-after-delta-bound}
\end{align}

Asymptotically, we choose smaller values of $\delta$ for larger number of
sensors. Hence, neglecting terms of order $\delta^3$, we tighten the bound by
choosing $\delta$ as a function of the remaining variables in order to have
$\sqrt{\frac{2nm\kappa^2\delta^2 }{\sigma^2}} = \frac{1}{2}$. This is achieved
for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2 w}}$, so that for
$\Phi(\delta) = \delta^2$, equation~\eqref{eq:lb-after-delta-bound} becomes
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2 w}.
\end{equation}
This completes the proof.
\end{IEEEproof}

>>>>

Mosher et.\ al.~\cite{Mosher1993Error} first propounded Cramer-Rao lower bounds
for unbiased source localization algorithms. Their work also forms the basis
for setting up the source localization problem and deriving more universally
applicable bounds in this paper. The Cramer-Rao lower bound is not in itself a
completely satisfactory answer to the question of fundamental limits for source
localization accuracy. This is because Cramer-Rao bounds only apply to unbiased
estimators (or to estimators of \emph{known} bias). In practice, however, many
popular source localization algorithms have been shown to be biased, e.g.\
the Minimum Norm Estimate (MNE)~\cite{Hamalainen1994Interpreting} is known to
bias the solution towards the surface of the head~\cite{Lin2006Assessing}. It
is also known that unbiased estimators can have worse mean-squared-error
performance than biased estimators. So Cramer-Rao bounds are useful only to a
degree, and there may be benefit in deriving bounds that hold for all
estimators.

@@

All signals on the aforementioned circular domain are of the form
$f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
represented by the impulse signal, $f(t;\theta) = \delta(t - \theta)$, where
$\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
through the diffusive medium, which, intuitively speaking, blurs the impulse.
More concretely, we assume that the medium is linear and shift-invariant, so
that it can be represented by a spatial impulse response (blurring would then
correspond to low-pass filtering). Let this impulse response be given by
$g(t)$. Then, the noiseless, continuous-space signal (post-filtering and
pre-sampling) is given by the convolution, $x(t; \theta) = (g*f)(t) = g(t -
\theta)$. Here, we further make the simplifying assumption that $g(t)$ has a
sufficiently restricted support, so that aliasing effects are avoided, and
$x(t; \theta)$ is always well-defined. To be precise, $g(t) = 0$ when $\abs{t}
> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < T / 2$
(the reason for the factor of $1/2$ will become clear in a later section).

@@

Consider the following estimation problem: we have $n$ i.i.d.\ random samples
$Y^n$ from a distribution $P$, which is indexed by a parameter $\theta \in
\Theta$.  Denote the set of these distributions by $\mathcal{P} = \{P(\theta) :
\theta \in \Theta\}$. Suppose we now wish to estimate $\theta$ from $Y^n$.
Define a loss metric $\rho(\theta, \hat\theta)$ (e.g.\ $\rho(\theta,
\hat\theta) = \abs{\theta - \hat\theta}$). For this metric, we can define the
minimax risk over all possible estimators $\hat\theta(Y^n)$ and all possible
$\theta \in \Theta$:
\begin{equation} \label{eq:minimax-expr}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \inf_{\hat\theta} \sup_{\theta \in \Theta} \mathbb E[\Phiorho (\hat\theta(Y^n), \theta)]
\end{equation}
where $\Phi$ is any non-decreasing function (e.g.\ $\Phi(\rho) = \rho^2$) and
$Y^n$ is the random vector corresponding to a noisy realization of sensor
values.

@@

We now need to lower bound the probability of error in the hypothesis testing
problem. The simplest way to do this is to consider a binary hypothesis test
($\abs{\mathcal{V}} = 2$) and use what is known as Le Cam's method:
\begin{theorem} \label{thm:le-cam}
	For a binary hypothesis test, i.e., when $\mathcal{V} = \{0, 1\}$,
	\begin{equation}
		\inf_\psi \mathbb P(\psi(Y^n) \neq V) = 1 - \norm{P_0 - P_1}_{TV}
	\end{equation}
	where $P_i$ is short-hand for $P(\theta_i)$ and $\norm{P_0 - P_1}_{TV}$ is
	the total variation distance between the two distributions, defined as
	$\norm{\cdot}_{TV} = \frac{1}{2} \norm{\cdot}_1$.
\end{theorem}
For a proof, we refer the reader to Proposition~2.11
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:le-cam} states
that the minimum probability of error that any estimator must make in a binary
hypothesis testing problem is related to the distance between the distributions
corresponding to the two hypotheses. The closer the two distributions, the
higher the chance of making an error in distinguishing between them.

@@

\begin{IEEEproof}
Starting from equation~\eqref{eq:le-cam-bound} and working on the setting
described in Section~\ref{sec:source-localization}, we proceed to derive the
total variation distance for the distributions of interest. Using Pinsker's
inequality~\cite{Pinsker} and the convenient tensorization of the
KL-divergence~\cite{tensorization}, we see that:
\begin{equation} \label{eq:pinsker-tensorization}
	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
\end{equation}
For multivariate normal distributions with the same covariance, the
KL-divergence is given by
\begin{equation} \label{eq:kl-div-normal}
	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
\end{equation}
where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
respectively~\cite{KLDivNormal}.

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{overlap-middle-pics}
	\caption{Depiction of the continuous-space signals produced by two
		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
		shifted impulse response, and therefore has a support of size $w$.
		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
		$\Theta$, so the signals are separated by a distance $2\delta$.}
	\label{fig:overlap-middle}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{delta-sampled-pics}
	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
		total size of the support of the difference signal is $w+2\delta$,
		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
		$\Delta(k)$ are non-zero.}
	\label{fig:delta-sampled}
\end{figure}

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kT}{m}; \theta_0\Big) - x\Big(\frac{kT}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(t;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
equal to the number of sensors in the total region covered by the signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{T} + 1}$, since at most a fraction $(w + 2\delta) / T$ of the $m$
sensors (plus 1, to account for edge-effects) can lie in the region covered by
the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
hence
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{T} + 1\Big).
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
example). In such a case, one part of the signal $x(t;\theta_0)$ will appear at
the left edge of the domain, and the repetition from the period $[T, 2T)$ will
appear at the right edge of the domain. Also note that the two signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most once, since $w < T/2$, as
stated in section~\ref{sec:signal-model}.

The upper bound in~\eqref{eq:delta-bound} translates into a lower
bound for~\eqref{eq:lb-after-pinsker}:
\begin{align}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n}{2\sigma^2 T} 4 \kappa^2 \delta^2 (w + 2\delta) m} \Bigg] \\
	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2nm \kappa^2 \delta^2 (w + 2\delta)}{\sigma^2 T}} \Bigg] \label{eq:lb-after-delta-bound}
\end{align}
Asymptotically, we choose smaller values of $\delta$ for larger number of
sensors. Hence, neglecting terms of order $\delta^3$, we tighten the bound by
choosing $\delta$ as a function of the remaining variables in order to have
$\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} = \frac{1}{2}$. This is
achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2 w}}$, so that for
$\Phi(\delta) = \delta^2$, equation~\eqref{eq:lb-after-delta-bound} becomes
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2 w}.
\end{equation}
This completes the proof.
\end{IEEEproof}

\section{Extensions}

\subsection{Linear domain (in place of a circle)}

So far, we've relied on the presence of a circular domain for to make the
arguments in the proof. However, the most important requirement was that
\emph{all} parts of the impulse response should get \emph{sensed} uniformly.
So, if $\theta$ were restricted to the region $[0, T)$ (now on a linear,
non-periodic domain), and if sensors were available to sense the signal from
$[-w/2, T{+}w/2)$ (for an impulse response with restricted support as described
in section~\ref{sec:signal-model}), then the proof for sensor noise would still
fall through, albeit with slightly different constants.

\subsection{From Lipschitz to $\alpha$-Holder continuous impulse responses}

We can trivially expand the domain of impulse responses to which the lower
bound applies to include $\alpha$-Holder continuous functions. These are
functions which satisfy
\begin{equation}
	\abs{g(u) - g(v)} \leq \kappa \norm{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
\end{equation}
for some constant $\kappa$, and for $\alpha > 0$.

\subsection{From a one-dimensional domain to a $d$-dimensional domain}

Another simple extension takes our problem from a one-dimensional setting to a
$d$-dimensional setting. Here, we would have $\v\theta \in [0, T)^d$, and the
$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
\vhat\theta}^2$. Then, using Assouad's method~\cite{Duchi2015Information}, we
can split the minimax risk along each of the $d$ dimensions, and bound each
separately using Le Cam's method.
